GRB Afterglows In The Multi-Messenger Era

### 2018-06-20 structuredJets.tex
Minor additions

@@

\begin{abstract}
Abstract abstract abstract.
\end{abstract}

\section{Introduction} \label{sec:intro}

@@

	We can obtain the temporal power law slope of the light curve by differentiating both Equations \eqref{eq:tobsPsi} and \eqref{eq:FnuPsi} with respect to $\psi$.  Noting that $dE/d\psi = -dE/d\theta$ we obtain for the individual derivatives:
\begin{eqnarray}
	\frac{d \log \tobs}{d \psi} = \frac{8}{3} \cot \psi - \frac{1}{3} \frac{d \log E}{d \theta}\ , \\
	\frac{d \log F_\nu}{d \psi} = \left(-s_1 + \frac{2}{3} s_2 +s_3+\beta\right)\cot \psi - \left(1+\frac{1}{3}s_3\right) \frac{d \log E}{d \theta}\ .
\end{eqnarray}
Taking the ratio and simplifying gives:
\begin{eqnarray}
	\frac{d \log F_\nu}{d \log \tobs}(\psi) = \frac{3 \beta - 3s_1 + 2s_2+3s_3 + g(\psi)}{ 8+g(\psi)} \\
	g(\psi) \equiv -\tan \psi \frac{d \log E}{d \theta}\ .
\end{eqnarray}
The parameter $g$ is directly measurable from the light curve, given the spectral information which fixes $\beta$, $s_1$, and $s_2$.

>>>>

\newcommand{\gwbns}{GW170817}

@@

\begin{abstract}
	Abstract abstract abstract
\end{abstract}

\section{Introduction} \label{sec:intro}
	The binary neutron star (BNS) merger \gwbns\ displayed many of the predicted electromagnetic counterparts.  Prompt gamma-ray emission in the form of a short gamma-ray burst (sGRB) in the first seconds after merger, an optical and infrared kilonova visible for hours and days, and a broadband synchrotron afterglow first observed 9 days after merger which may remain visible for a year or more.

	While this event qualitatively matched the community's expectations, the details of the emission from each counterpart were very unexpected.  The sGRB was delayed by $1.7$s after the GW chirp and was the lowest luminosity sGRB ever observed, the kilonova contained a rapidly varying blue component in tension with numerical models, and the afterglow demonstrated a long power-law \emph{rise} for roughly 150 days, a feature never before seen in GRB afterglows.

	In this paper we discuss this new \emph{structured} phase of GRB afterglow evolution and its interpretation in terms of dynamics of a relativistic blast wave.  We provide analytic formula for the start and end times of this phase and for the approximate power-law slope of the light curve.  The approximate analytic formula are validated by a numerical model which we have made publicly available.

\section{The Single Shell Framework}

	GRB afterglows are synchrotron radiation emitted from a relativistic blast wave propagating through the GRB circumburst medium, which we take to be a uniform ISM.  Models of this process have two components: the hydrodynamics of the blast wave and the radiative transfer of the synchrotron radiation.

	We describe both components with a trans-relativistic single shell model (CITE Hendrik's review).  In such a model the blast wave is approximated as a homogenous slab of hot plasma comprising both the forward shock and contact discontinuity.  The Rankine-Huginot (CITE RH) shock jump conditions can be used to write all other fluid variables in terms of external quantities and the fluid four-velocity $u$.

	The blast wave is comprised of two components, prompt ejecta with mass \Mej and shocked ISM with energy density $\tau$, radial width $\Delta r$, and angular width $\Delta \Omega$. Both components share a four-velocity $u$ and expand into a medium of constant density $\rho_0$.

@@

	We can obtain the temporal power law slope of the light curve by differentiating both Equations \eqref{eq:tobsPsi} and \eqref{eq:FnuPsi} with respect to $\psi$.  Noting that $dE/d\psi = -dE/d\theta$ we obtain for the individual derivatives:
\begin{eqnarray}
	\frac{d \log \tobs}{d \psi} = \frac{8}{3} \cot \psi - \frac{1}{3} \frac{d \log E}{d \theta}\ , \\
	\frac{d \log F_\nu}{d \psi} = \left(-s_1 + \frac{2}{3} s_2 +s_3+\beta\right)\cot \psi - \left(1+\frac{1}{3}s_2\right) \frac{d \log E}{d \theta}\ .
\end{eqnarray}
Taking the ratio and simplifying gives:
\begin{eqnarray}
	\frac{d \log F_\nu}{d \log \tobs}(\psi) = \frac{3 \beta - 3s_1 + 2s_2+3s_3 + (3+s_2)g(\psi)}{ 8+g(\psi)} \\
	g(\psi) \equiv -\tan \psi \frac{d \log E}{d \theta}\ .
\end{eqnarray}
The parameter $g$ is directly measurable from the light curve, given the spectral information which fixes $\beta$, $s_1$, and $s_2$.
